Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-11-09 analysis/paper/paper.qmd
added references related to GIS map
tried Tukey's HSD

summary(aov(min_tcsa ~ as.factor(ecoregion), points_in_veg_zones_all))

@@

summary(aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest_box))

@@

>>>>

eco_aov <- aov(min_tcsa ~ as.factor(ecoregion), points_in_veg_zones_all)
summary(eco_aov)
eco_tur<- TukeyHSD(eco_aov)
# plot(eco_tur)

@@

for_aov <- aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest_box)
summary(for_aov)
for_tur<- TukeyHSD(for_aov)
# plot(for_tur)

@@

Map A. @yim1975distribution, modified by @yi2010vegetation

Map B. @lee2008relationship
